\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-10-26 paper.tex
Tweak wording

\subsubsection{Broker}
Brokers represent data providers and consumers to deal with the trading process and publish the provider’s data streams as brokers are expected to have higher resource. Brokerage fees for each product will be charged by the broker.

@@

\subsection{Components}
\subsubsection{Masked Authenticated Messaging}
MAM is a second layer data communication protocol built on the feeless and scalable IOTA network. It resolves the challenges to publish encrypted streaming data to the distributed ledgers with session keys to channel, which indicates that each address is derived from its previous one. In other words, with channel root (a.k.a., the first message of a channel) and its session key, all data becomes accessible and validatable. Furthermore, each user can create multiple channels as possible.

@@

\subsubsection{Ethereum Smart Contract}
Smart contract is a protocol for formulating agreement on a blockchain that provides verification and execution of the contract. All conditions and states established in the contract are enforeced with transparency. The appearance of smart contracts meet different requirements of trading pattern.

\subsubsection{Blind Signature}
Blind signature\cite{blindSig} is used to prevent the situation that the a broker would stole data if a session key is not encryted. In fact, blind signature is a form of digital signature where the message is first "blinded" by a random "blinding factor", and then passed to a signer to confirm. The encrypted message, along with the blinding factor, can be later verified with the signer’s public key.

@@

\subsection{Game Theory Evaluation}
Game Theory is a methodology to discuss strategic interaction among game players. We can ensure the sustainability of decentralized data marketplace by proving the existence of Nash Equilibrium at a certain acceptable range. Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models in data pricing, and we employ repeated games which fits the scenario of data subscription to build our game theory model.

>>>>

\subsubsection{Broker}
Brokers represent data providers and consumers to deal with the trading process and publish the provider's data streams as brokers are expected to have higher resource. Brokerage fees for each product will be charged by the broker.

@@

\subsection{Components}
\subsubsection{Masked Authenticated Messaging}
MAM is a second layer data communication protocol built on the IOTA peer-to-peer network infrastructure, the Tangle. It resolves the challenges to publish encrypted streaming data to the distributed ledgers with session keys to channel, which indicates that each address is derived from its previous one. In other words, with channel root (a.k.a., the first message of a channel) and its session key, all data becomes accessible and validatable. Furthermore, each user can create multiple channels as possible.

@@

\subsubsection{Ethereum Smart Contract}
Smart contract is a protocol for formulating agreement on a DLT/blockchain that provides verification and execution of the contract. All conditions and states established in the contract are enforeced with transparency. The appearance of smart contracts meet different requirements of trading pattern.

\subsubsection{Blind Signature}
Blind signature\cite{blindSig} is used to prevent the situation that the a broker would stole data if a session key is not encryted. In fact, blind signature is a form of digital signature where the message is first "blinded" by a random "blinding factor", and then passed to a signer to confirm. The encrypted message, along with the blinding factor, can be later verified with the signer's public key.

@@

\subsection{Game Theory Evaluation}
Game Theory is a methodology to discuss strategic interaction among game players. We can ensure the sustainability of decentralized data marketplace by proving the existence of Nash Equilibrium at a certain acceptable range. Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models in data pricing, and we employ repeated games which fits the scenario of data subscription to build our model.
